---
title: "Week 6 HW Part 3"
format: html
warning: false
messages: false
editor_options: 
  chunk_output_type: console
---

# Who were the winners?

At the conclusion of the ASDN project the PIs decided to hand out first, second, and third prizes to the observers who measured the most eggs. Who won?

## Setup

```{r}
library(tidyverse)
library(DBI)
library(duckdb)
library(dplyr)
```

## Connect to database

```{r}
conn <- DBI::dbConnect(duckdb::duckdb(), dbdir='database.db')
```

## Load tables

To have observer full name and the number of eggs they measured, we need the Personnel table, the Bird_egg table for egg measurement, and the Bird_nests table to connect the two.

**Note:** Bird_nests has a column, Clutch_max, that contains the maximum number of eggs recorded for each nest. To me, that is unclear if the observer actually measured each egg in the nest. But, I know for sure that each egg in the Bird_egg table was measured, so I will use counts from that table to answer this question.

```{r}
# Personnel table
personnel <- tbl(conn, "Personnel")

# Nests table
nests <- tbl(conn, "Bird_nests")

# Eggs table
eggs <- tbl(conn, "Bird_eggs")
```

## Query

```{r}
egg_nest <- left_join(eggs, nests, by = "Nest_ID")

all <- left_join(egg_nest, personnel, by = join_by(Observer == Abbreviation)) |>
    group_by(Name) |>
    summarise(total_eggs = n()) |>
    ungroup() |>
    arrange(desc(total_eggs)) |>
    head(3) |>
    show_query()

print(all)
```

## Discussion

I did use multiple R statements to get the answer. dbplyr did not create a temp table, but instead made a nested query. 

It limited the first 3 rows using a SQL LIMIT clause. 




